Hijacking Simulators with Universal Probabilistic Programming

### 2019-05-20 paper/neurlps2019/main.tex
updated

% \end{itemize}
\begin{wrapfigure}{R}{0.45\textwidth}
\centering
% \includegraphics[width=0.35\textwidth]{../plots/mpenny-pop10/mpenny_10.pdf}
\includegraphics[width=0.40\textwidth]{../plots/model_lambda/model_posterior.pdf}
\includegraphics[width=0.40\textwidth]{../plots/model_lambda/hist_posteriors.png}
\caption{Hijacking the OpenMalaria simulator}
\label{fig:hijacking} 
\end{wrapfigure}

% One powerful \emph{class} of models are simulators. 
Simulators are useful tools when conducting experiments in the real system 
is impossible, or impractical and they arise in numerous industrial \cite{di2015simulator,judd2009numerically,kass1990rapid} and scientific applications~\cite{smith2008towards,bershteyn2018implementation,gleisberg_event_2008} . They are rich models and encode years, if not decades, of research and development.
The \emph{model}, or equivalently \emph{program}, specified by the simulator defines a joint density $p(x,y)$ and the inputs into the simulator denote priors, $p(x)$.

 def that are difficult to generate represent a large class of generative models, where the simulator itself represents a joint density
$p(x|y)$  arise in many industrial
Thus, Simulators by their very nature are
information rich and naturally describe complicated joint densities.
However, in order to write a simulator in a standard probabilistic programming set-up one would have to re-write a simulator in the language of the probabilistic programming system (PPS), which 
in many cases is not feasible, nor efficient due to both the size 
and complexity of the simulator code base. 
However, what if one could arbitrary connect a simulator, written in any
language and connect it directly to a PPS, without having to re-write
the simulator in the given PPS?

>>>>

% \end{itemize}
\begin{wrapfigure}{R}{0.44\textwidth}
\centering
% \includegraphics[width=0.35\textwidth]{../plots/mpenny-pop10/mpenny_10.pdf}
\includegraphics[width=0.40\textwidth]{../plots/model_lambda/model_posterior.pdf}
\includegraphics[width=0.40\textwidth]{../plots/model_lambda/hist_posteriors.png}
\caption{Hijacking the OpenMalaria simulator}
\label{fig:hijacking} 
\end{wrapfigure}

% One powerful \emph{class} of models are simulators. 
Simulators are useful tools when conducting experiments in the real system 
is impossible, or impractical and they arise in numerous industrial \cite{di2015simulator,judd2009numerically,kass1990rapid} and scientific applications~\cite{smith2008towards,bershteyn2018implementation,gleisberg_event_2008} . They are rich models and encode years, if not decades, of research and development.
Thus, Simulators by their very nature are
information rich and naturally describe complicated joint densities.
That is the \emph{model}, or equivalently \emph{program}, specified by the simulator defines a joint density $p(x,y)$ and the inputs into the simulator denote priors, $p(x)$.

However, in order to write a simulator in a standard probabilistic programming set-up one would have to re-write a simulator in the language of the probabilistic programming system (PPS), which 
in many cases is not feasible, nor efficient due to both the size 
and complexity of the simulator code base. 
However, what if one could arbitrary connect a simulator, written in any
language and connect it directly to a PPS, without having to re-write
the simulator in the given PPS?
